plot_weight_length_cf

### 2022-03-01 smelt_2019_allseasons/plot_weight_length_cf.Rmd
Updated code to change Mesh to enclosure type and add the delta symbol

```{r}
smeltdata <- read_csv("data_clean/clean_smelt_cf_2019.csv", col_types = cols(.default="f", FL_cm = "d", Weight_g = "d", K = "d", ID = "c"))
glimpse(smeltdata)
```

>>>>

```{r}
library(dplyr)
library(ggplot2)
library(readr)
library(here)
```

```{r}
smeltdata <- read_csv(here("smelt_2019_allseasons", "data_clean", "clean_smelt_cf_2019.csv"), col_types = cols(.default="f", FL_cm = "d", Weight_g = "d", K = "d", ID = "c"))
glimpse(smeltdata)
```
